Paper notes

### 2019-08-28 paper_notes.Rmd
check formula, no M value, simplify ethnic

  f_eth <- function(i_e,M,x,n,S){
   if (x > n){
     U <- NA}else{
     if (x < (n*i_e)){
   U <- (x / (n*i_e)) * S
      }else if (x > (n*i_e)){
         U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
        }else{
     U <- 1}
        round(U,digits = 3)
      }
 }

@@

f_val <- function(e_w,ew_ng,i_v,S_v){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- ((1-(round(abs(e_w-ew_ng), digits=2)))/(1-i_v)) * S_v
      }
  round(U,digits = 3)
  }

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 1

fvf0p  <- f_val(e_w,0,i_v,S_v)
fvf1p  <- f_val(e_w,0.1,i_v,S_v)
fvf2p   <- f_val(e_w,0.2,i_v,S_v)
fvf3p   <- f_val(e_w,0.3,i_v,S_v)
fvf4p   <- f_val(e_w,0.4,i_v,S_v)
fvf5p   <- f_val(e_w,0.5,i_v,S_v)
fvf6p   <- f_val(e_w,0.6,i_v,S_v)
fvf7p   <- f_val(e_w,0.7,i_v,S_v)
fvf8p   <- f_val(e_w,0.8,i_v,S_v)
fvf9p  <- f_val(e_w,0.9,i_v,S_v)
fvf10p  <- f_val(e_w,1.0,i_v,S_v)

@@

fvf0t <- f_val(e_w,0,i_v,S_v)
fvf1t  <- f_val(e_w,0.1,i_v,S_v)
fvf2t   <- f_val(e_w,0.2,i_v,S_v)
fvf3t   <- f_val(e_w,0.3,i_v,S_v)
fvf4t   <- f_val(e_w,0.4,i_v,S_v)
fvf5t   <- f_val(e_w,0.5,i_v,S_v)
fvf6t  <- f_val(e_w,0.6,i_v,S_v)
fvf7t   <- f_val(e_w,0.7,i_v,S_v)
fvf8t   <- f_val(e_w,0.8,i_v,S_v)
fvf9t  <- f_val(e_w,0.9,i_v,S_v)
fvf10t  <- f_val(e_w,1.0,i_v,S_v)

@@

@@

i_e = 0.6   # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0     # Linear + Constant function = S=1,M=1
n = 8     # Schelling Threshold function = S=0,M=1

@@

e_w <- 0.5    # parameters to manipulate
i_v <- 0.2    # Symmetric = S:1,M:0/Threshold = S:0
S_v  <- 0
M <-  0

fv0d2 <- f_val(e_w,0,M,i_v,S_v)             # value utility for each option, 
fv1d2 <- f_val(e_w,0.1,M,i_v,S_v)           # increasing nuMber is average ethnic weight of neighborhood j
fv2d2 <- f_val(e_w,0.2,M,i_v,S_v)
fv3d2 <- f_val(e_w,0.3,M,i_v,S_v)
fv4d2 <- f_val(e_w,0.4,M,i_v,S_v)
fv5d2 <- f_val(e_w,0.5,M,i_v,S_v)
fv6d2 <- f_val(e_w,0.6,M,i_v,S_v)
fv7d2 <- f_val(e_w,0.7,M,i_v,S_v)
fv8d2 <- f_val(e_w,0.8,M,i_v,S_v)
fv9d2 <- f_val(e_w,0.9,M,i_v,S_v)
fv10d2 <- f_val(e_w,1.0,M,i_v,S_v)

@@

report_V <- na.omit(data.frame(M,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r","M =", M,"; ", "S = ",S_v)

>>>>

  f_eth <- function(i_e,M,x,n,S){
   if (x > n){
     U <- NA}else{
     if (x <= (n*i_e)){
   U <- (x / (n*i_e)) * S
      }else {
         U <- M + ((1- (x/n))*(1-M))/(1-i_e) 
        }
        round(U,digits = 3)
      }
 }

@@

f_val <- function(e_w,ew_ng,i_v,S_v,Mv){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- (Mv + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-Mv))/(1-i_v)) * S_v
        # (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S
      }
  round(U,digits = 3)
  }

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 1
Mv <- 0

fvf0p  <- f_val(e_w,0,i_v,S_v,Mv)
fvf1p  <- f_val(e_w,0.1,i_v,S_v,Mv)
fvf2p   <- f_val(e_w,0.2,i_v,S_v,Mv)
fvf3p   <- f_val(e_w,0.3,i_v,S_v,Mv)
fvf4p   <- f_val(e_w,0.4,i_v,S_v,Mv)
fvf5p   <- f_val(e_w,0.5,i_v,S_v,Mv)
fvf6p   <- f_val(e_w,0.6,i_v,S_v,Mv)
fvf7p   <- f_val(e_w,0.7,i_v,S_v,Mv)
fvf8p   <- f_val(e_w,0.8,i_v,S_v,Mv)
fvf9p  <- f_val(e_w,0.9,i_v,S_v,Mv)
fvf10p  <- f_val(e_w,1.0,i_v,S_v,Mv)

@@

fvf0t <- f_val(e_w,0,i_v,S_v,Mv)
fvf1t  <- f_val(e_w,0.1,i_v,S_v,Mv)
fvf2t   <- f_val(e_w,0.2,i_v,S_v,Mv)
fvf3t   <- f_val(e_w,0.3,i_v,S_v,Mv)
fvf4t   <- f_val(e_w,0.4,i_v,S_v,Mv)
fvf5t   <- f_val(e_w,0.5,i_v,S_v,Mv)
fvf6t  <- f_val(e_w,0.6,i_v,S_v,Mv)
fvf7t   <- f_val(e_w,0.7,i_v,S_v,Mv)
fvf8t   <- f_val(e_w,0.8,i_v,S_v,Mv)
fvf9t  <- f_val(e_w,0.9,i_v,S_v,Mv)
fvf10t  <- f_val(e_w,1.0,i_v,S_v,Mv)

@@

## Single Run
```{r single-run,fig.width=4,fig.height= 3, fig.align="center", include=TRUE, echo=FALSE}

e_w = 0.875
  v_w = 1-e_w
ew_ng_curr = 0.933
ew_ng_alt = 0.906
i_e = 0.5
S = 1
M = 0
i_v = 0.1
S_v = 0
k = 2
n_curr = 8
  eth_curr = 5
n_alt = 7
  eth_alt = 4

param_eth <- k * e_w
param_val <- k * v_w

dist_curr <- abs(ew_ng_curr - e_w)
  dist_alt <- abs(ew_ng_alt - e_w)

conc_curr <- (eth_curr / n_curr)
conc_alt <- (eth_alt / n_alt)

uti_eth_curr <- f_eth(i_e,M,eth_curr,n_curr,S)
uti_eth_alt <- f_eth(i_e,M,eth_alt,n_alt,S)

uti_val_curr <- f_val(e_w,ew_ng_curr,i_v,S_v)
uti_val_alt <- f_val(e_w,ew_ng_alt,i_v,S_v)

diff_eth <- (uti_eth_alt - uti_eth_curr)
  diff_val <- (uti_val_alt - uti_val_curr )

prob_one_run <- prob(diff_eth,diff_val,e_w,v_w,k)

report_one_run <- na.omit(data.frame(param_eth,param_val,i_e,i_v,S,M,dist_curr,dist_alt,conc_curr,conc_alt,uti_eth_curr,uti_eth_alt,uti_val_curr,uti_val_alt,prob_one_run))

suppressWarnings(suppressMessages(
knitr::kable(report_one_run,align="c")
))

@@

i_e = 0.3   # parameters to manipulate
S = 1     # Symmetric single-peaked function: S=1,M=0
M = 0     # Linear + Constant function = S=1,M=1
n = 8     # Schelling Threshold function = S=0,M=1

@@

e_w <- 0.5    # parameters to manipulate
i_v <- 0.0    # Symmetric = S:1,M:0/Threshold = S:0
S_v  <- 1
Mv <- 0

fv0d2 <- f_val(e_w,0,i_v,S_v,Mv)             # value utility for each option, 
fv1d2 <- f_val(e_w,0.1,i_v,S_v,Mv)           # increasing nuMber is average ethnic weight of neighborhood j
fv2d2 <- f_val(e_w,0.2,i_v,S_v,Mv)
fv3d2 <- f_val(e_w,0.3,i_v,S_v,Mv)
fv4d2 <- f_val(e_w,0.4,i_v,S_v,Mv)
fv5d2 <- f_val(e_w,0.5,i_v,S_v,Mv)
fv6d2 <- f_val(e_w,0.6,i_v,S_v,Mv)
fv7d2 <- f_val(e_w,0.7,i_v,S_v,Mv)
fv8d2 <- f_val(e_w,0.8,i_v,S_v,Mv)
fv9d2 <- f_val(e_w,0.9,i_v,S_v,Mv)
fv10d2 <- f_val(e_w,1.0,i_v,S_v,Mv)

@@

report_V <- na.omit(data.frame(Mv,S_v,des_dist,ew_agent,mean_ew_ng,Utility_V))

title_cond_V <- paste0("Ethnic weight i = ", e_w,"; desired distance i = ",i_v,"\n\r", "S = ",S_v)
